---
title: "Bush-Francis Catatonia Rating Scale"
output:
  html_document:
    toc: FALSE
    css: _site/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("utils.R")
```

```{r}
# place post image
post_image(img_path = "images/bfcrs_catatonia.png")
```

**[Download Flashcards](flashcards/bfcrs_20240301.apkg)** for Anki, with three separate card types:

* General information about the BFCRS as cloze deletions
* BFCRS Items asking for item description, examples, and scoring 
* Differences between items of the BFCRS to help clarify nuances between domains

## Scoring BFCRS Items {.tabset}

Items are scored 0, 1, 2, or 3

Except for several dichotomous items scored *either* 0 or 3  
(Waxy Flexibility, Mitgehen, Gegenhalten, Ambitendency, Grasp Reflex, Perseveration)

### Simple Text

Useful for pasting into EMRs, especially those like CPRS with monospaced typewriter fonts (e.g., Courier, Menlo, Consolas)

```
Time and Date:

|            BFCRS Items | 0 | 1 | 2 | 3 |
|------------------------|---|---|---|---|
|             Excitement |   |   |   |   |
|    Immobility / Stupor |   |   |   |   |
|                 Mutism |   |   |   |   |
|                Staring |   |   |   |   |
|  Posturing / Catalepsy |   |   |   |   |
|              Grimacing |   |   |   |   |
| Echopraxia / Echolalia |   |   |   |   |
|             Stereotypy |   |   |   |   |
|             Mannerisms |   |   |   |   |
|          Verbigeration |   |   |   |   |
|               Rigidity |   |   |   |   |
|             Negativism |   |   |   |   |
|       Waxy Flexibility |   | - | - |   |
|             Withdrawal |   |   |   |   |
|            Impulsivity |   |   |   |   |
|    Automatic Obedience |   |   |   |   |
|               Mitgehen |   | - | - |   |
|            Gegenhalten |   | - | - |   |
|           Ambitendency |   | - | - |   |
|           Grasp Reflex |   | - | - |   |
|          Perseveration |   | - | - |   |
|          Combativeness |   |   |   |   |
|  Autonomic Abnormality |   |   |   |   |

```

### HTML Table

Formatted table, easily pasted into spreadsheets like Excel or Sheets

Time and Date:

| BFCRS Items            | 0 | 1 | 2 | 3 |
|-----------------------:|:-:|:-:|:-:|:-:|
|             Excitement |   |   |   |   |
|    Immobility / Stupor |   |   |   |   |
|                 Mutism |   |   |   |   |
|                Staring |   |   |   |   |
|  Posturing / Catalepsy |   |   |   |   |
|              Grimacing |   |   |   |   |
| Echopraxia / Echolalia |   |   |   |   |
|             Stereotypy |   |   |   |   |
|             Mannerisms |   |   |   |   |
|          Verbigeration |   |   |   |   |
|               Rigidity |   |   |   |   |
|             Negativism |   |   |   |   |
|       Waxy Flexibility |   | - | - |   |
|             Withdrawal |   |   |   |   |
|            Impulsivity |   |   |   |   |
|    Automatic Obedience |   |   |   |   |
|               Mitgehen |   | - | - |   |
|            Gegenhalten |   | - | - |   |
|           Ambitendency |   | - | - |   |
|           Grasp Reflex |   | - | - |   |
|          Perseveration |   | - | - |   |
|          Combativeness |   |   |   |   |
|  Autonomic Abnormality |   |   |   |   |

## Descriptions of Scoring the BFCRS Items

[This PDF Manual by the University of Rochester](https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/about/docs/BFCRS-with-Manual-links.pdf) is useful to print and take into patient rooms while learning to score the BFCRS.

In-depth descriptions and examples of each item are available in the [BFCRS Training Manual by the University of Rochester](https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/documents/BFCRS-Training-Manual-22-02-24.pdf).

The tabulated information for scoring the BFCRS below is an even more concise reference.

| BFCRS Items            | 0      | 1                                                                                       | 2                                                     | 3                                                                |
| ---------------------- | ------ | --------------------------------------------------------------------------------------- | ----------------------------------------------------- | ---------------------------------------------------------------- |
| Excitement             | Absent | Excessive motion, intermittent                                                          | Constant motion, hyperkinetic without rest periods    | Full-blown catatonic excitement, endless frenzied motor activity |
| Immobility / Stupor    | Absent | Sits abnormally still, may interact briefly                                             | Virtually no interaction with external world          | Stuporous (psychological), non-reactive to painful stimuli       |
| Mutism                 | Absent | Verbally unresponsive to majority of questions; incomprehensible whisper                | Speaks < 20 words in 5 minutes                        | No speech                                                        |
| Staring                | Absent | < 20 sec b/w shifting of attention, poor eye contact, repeated gaze, decreased blinking | \> 20 sec gaze held, occasionally shifts attention    | Fixed gaze, non-reactive                                         |
| Posturing / Catalepsy  | Absent | < 1 minute                                                                              | \> 1 minute, < 15 minutes                             | Bizarre posture, or mundane maintained ≥ 15 min                  |
| Grimacing              | Absent | < 10 sec                                                                                | < 1 min                                               | Bizarre expression(s) maintained > 1 min                         |
| Echopraxia / Echolalia | Absent | Occasional                                                                              | Frequent                                              | Constant                                                         |
| Stereotypy             | Absent | Occasional                                                                              | Frequent                                              | Constant                                                         |
| Mannerisms             | Absent | Occasional                                                                              | Frequent                                              | Constant                                                         |
| Verbigeration          | Absent | Occasional                                                                              | Frequent, difficult to interrupt                      | Constant                                                         |
| Rigidity               | Absent | Mild resistance                                                                         | Moderate resistance                                   | Severe resistance, cannot be repostured                          |
| Negativism             | Absent | Mild resistance, occasionally contrary                                                  | Moderate resistance, frequently contrary              | Severe resistance, continually contrary                          |
| Waxy Flexibility       | Absent | –                                                                                       | –                                                     | Present                                                          |
| Withdrawal             | Absent | Minimal PO intake/interaction < 1 day                                                   | Minimal PO intake/interaction > 1 day                 | No PO intake/interaction for ≥ 1 day                           |
| Impulsivity            | Absent | Occasional                                                                              | Frequent                                              | Constant                                                         |
| Automatic Obedience    | Absent | Occasional                                                                              | Frequent                                              | Constant                                                         |
| Mitgehen               | Absent | –                                                                                       | –                                                     | Present                                                          |
| Gegenhalten            | Absent | –                                                                                       | –                                                     | Present                                                          |
| Ambitendency           | Absent | –                                                                                       | –                                                     | Present                                                          |
| Grasp Reflex           | Absent | –                                                                                       | –                                                     | Present                                                          |
| Perseveration          | Absent | –                                                                                       | –                                                     | Present                                                          |
| Combativeness          | Absent | Occasionally strikes out, low potential for injury                                      | Frequently strikes out, moderate potential for injury | Serious danger to others                                         |
| Autonomic Abnormality  | Absent | Abnormality of 1 parameter (exclude pre-existing hypertension)                          | Abnormality of 2 parameters                           | Abnormality of 3 or greater parameters                           |

## References

* Oldham, M. A. <a href="https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/about/docs/BFCRS-with-Manual-links.pdf">Bush-Francis Catatonia Rating Scale</a>
* Oldham, M. A. <a href="https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/documents/BFCRS-Training-Manual-22-02-24.pdf">Bush-Francis Catatonia Rating Scale Training Manual and Coding Guide</a> (2022)
* Wortzel, J. <a href="https://www.urmc.rochester.edu/psychiatry/divisions/collaborative-care-and-wellness/bush-francis-catatonia-rating-scale.aspx">Bush-Francis Catatonia Rating Scale Assessment Resources</a> University of Rochester Medical Center
* Chase, R. H. <a href="https://www.flickr.com/photos/internetarchivebookimages/14596961729/">Mental Medicine and Nursing: For Use in Training-Schools for Nurses and in Medical Classes and a Ready Reference for the General Practitioner</a> (1915)
