---
title: "Bush-Francis Catatonia Rating Scale"
output:
  html_document:
    toc: FALSE
    css: _site/style.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("utils.R")
```

```{r}
# place post image
post_image(img_path = "images/bfcrs_catatonia.png")
```

[Spreadsheet](https://docs.google.com/spreadsheets/d/1KX5Xa-X_lzhe8LmV23KTJwCSYazz_GA9q8CThxMck7Q/edit) in progress

## HTML Table

| BFCRS Item            | 0 | 1 | 2 | 3 |
|-----------------------|---|---|---|---|
| Excitement            |   |   |   |   |
| Immobility/Stupor     |   |   |   |   |
| Mutism                |   |   |   |   |
| Staring               |   |   |   |   |
| Posturing / Catalepsy |   |   |   |   |
| Grimacing             |   |   |   |   |
| Echopraxia/Echolalia  |   |   |   |   |
| Stereotypy            |   |   |   |   |
| Mannerisms            |   |   |   |   |
| Verbigeration         |   |   |   |   |
| Rigidity              |   |   |   |   |
| Negativism            |   |   |   |   |
| Waxy Flexibility      |   | - | - |   |
| Withdrawal            |   |   |   |   |
| Impulsivity           |   |   |   |   |
| Automatic Obedience   |   |   |   |   |
| Mitgehen              |   | - | - |   |
| Gegenhalten           |   | - | - |   |
| Ambitendency          |   | - | - |   |
| Grasp Reflex          |   | - | - |   |
| Perseveration         |   | - | - |   |
| Combativeness         |   |   |   |   |
| Autonomic Abnormality |   |   |   |   |

## References

* Oldham, M. A. <a href="https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/about/docs/BFCRS-with-Manual-links.pdf">Bush-Francis Catatonia Rating Scale</a>
* Oldham, M. A. <a href="https://www.urmc.rochester.edu/MediaLibraries/URMCMedia/psychiatry/documents/BFCRS-Training-Manual-22-02-24.pdf">Bush-Francis Catatonia Rating Scale Training Manual and Coding Guide</a> (2022)
* Wortzel, J. <a href="https://www.urmc.rochester.edu/psychiatry/divisions/collaborative-care-and-wellness/bush-francis-catatonia-rating-scale.aspx">Bush-Francis Catatonia Rating Scale Assessment Resources</a> University of Rochester Medical Center
* Chase, R. H. <a href="https://www.flickr.com/photos/internetarchivebookimages/14596961729/">Mental Medicine and Nursing: For Use in Training-Schools for Nurses and in Medical Classes and a Ready Reference for the General Practitioner</a> (1915)
